---
title: "Lake Selection"
author: "Denver Link, Mike Verhoeven"
date: "2024-06-21"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Objective
Assemble a dataset of lakes that shows fish survey, zoop survey, clarity, temp, WAE CPUE, Centrarchid CPUE

## To do list
- get the 2023 fishery surveyed lakes and add these to the fish surveys plan
- improve the zoop sampling data to understand what's had or getting a monthly zoop set
- check DOWs in DNR survey list for connection to other WBs
- get AIS species into the spreadsheet
- updated lakes and info from the lake chooser spreadsheet



#lake parameters plots:
-initially joined clarity/temp data together by DOW and basin ID - missed several lakes due to nhd to basin crosswalk
      -currently use nhdid level info to generate plots - better joining coverage
      -most coverage issues(9 waterbodies) seem to stem from 1. border lakes 2. reservoirs 3. very small

#Library
```{r}
library(tidyverse)
library(mnsentinellakes)
library(ggthemes)
library(arrow)
library(mwlaxeref)
library(plotly)
library(htmlwidgets)
library(data.table)
```

#Data
```{r}
#2024 DNR lakes
survey <- read_csv("scripts&data/data/input/DNR_lakes_filtered.csv") %>% 
  mutate(DOW = ifelse(DOW == "62005900", "62005600", DOW)) %>% 
  mutate(lake_id = str_replace_all(DOW, "-", ""),
         lake_id = case_when(nchar(lake_id) == 7 ~ paste0("0", lake_id), 
                             TRUE ~ lake_id),
         parent_dow = str_sub(lake_id, 1,6),
         basin_id = str_sub(lake_id, -2)) %>%
  local_to_nhdhr(from_colname = "lake_id", states = "mn") %>% 
  rename(site_id = nhdhr.id)

#9 lakes did not pick up nhdids - a few notable lakes (lake pepin, st louis river estuary, )
survey %>% 
  filter(is.na(site_id)) %>% 
  select(area_name, waterbody_name, DOW, survey_type, survey_components_proposed, notes, lake_id)



#fisheries data
cpe <- read_csv("scripts&data/data/input/MN_all_cpue_filtered.csv") %>% 
  mutate(lake_id = as.character(lake_id)) %>% 
  select(state, lake_name, lake_id, date_survey, year, month, sampling_method, species_1, total_effort_1, count, cpue) %>% 
  filter(sampling_method %in% c("Standard gill net sets", "Standard 3/4-in mesh, double frame trap net sets")) %>% 
  filter(species_1 != "cisco" & species_1 != "smallmouth_bass") %>% 
  #fixing dow
  mutate(lake_id = case_when(nchar(lake_id) == 7 ~ paste0("0", lake_id), 
                             TRUE ~ lake_id),
         parent_dow = str_sub(lake_id, 1,6),
         basin_id = str_sub(lake_id, -2)) %>% 
  rename(date = date_survey)


secchi <- read_csv("scripts&data/data/input/WQP_secchi_pull_20Mar2024.csv") %>% 
  select(MonitoringLocationIdentifier,
         ActivityStartDate,
         ResultMeasureValue,
         ResultMeasure.MeasureUnitCode) %>% 
  mutate(ResultMeasureValue = as.numeric(ResultMeasureValue)) %>% 
  filter(!is.na(ResultMeasureValue) & ResultMeasureValue >= 0) %>% 
  #Taking only MNPCA data and extracting DOW from monitoring location
  filter(str_detect(MonitoringLocationIdentifier, "^MNPCA-\\d{2}-\\d{4}-\\d{2}-\\d{3}$")) %>%
  mutate(DOW = str_replace_all(str_extract(MonitoringLocationIdentifier, "(?<=MNPCA-)\\d{2}-\\d{4}-\\d{2}"), "-", "")) %>% 
  #only keeping meter values
  filter(ResultMeasure.MeasureUnitCode == "m") %>% 
  local_to_nhdhr(from_colname = "DOW", states = "mn") %>% 
  rename(secchi_meters = ResultMeasureValue,
         date = ActivityStartDate,
         site_id = nhdhr.id) %>%
  mutate(year = year(date),
         month = month(date)) %>% 
  select(site_id,
         DOW,
         year,
         month, 
         secchi_meters) %>% 
  mutate(parent_dow = str_sub(DOW, 1,6),
         basin_id = str_sub(DOW, -2)) %>%
  #creating values for this analysis 
  filter(year >= 2000 & month %in% c("6", "7", "8")) %>% 
  group_by(site_id) %>% 
  summarise(med_summer_secchi_meters = median(secchi_meters))


temp <- read_feather("scripts&data/data/input/lake_temperature_metrics_GLM_NLDAS.feather", col_select = NULL, as_data_frame = TRUE, mmap = TRUE) %>%
  select(site_id, year, mean_surf_jul) %>% 
  mutate(site_id = str_remove(site_id, "^nhdhr_")) %>% 
  filter(year >= 2000) %>% 
  group_by(site_id) %>% 
  summarise(med_jul_temp = median(mean_surf_jul))

glm <- read_csv("scripts&data/data/input/glm_lake_metadata.csv") %>% 
  filter(state == "MN") %>% 
  select(site_id, lake_name, centroid_lon, centroid_lat, max_depth, area) %>% 
  mutate(site_id = str_remove(site_id, "^nhdhr_")) 
#nhdhr level info - code in "old code" section to read in by DOW

zoops <- read_csv("scripts&data/data/input/ZoopDB_lake_effort_20240402.csv") %>% 
  mutate(dowlknum = as.character(dowlknum),
         lake_id = case_when(nchar(dowlknum) == 7 ~ paste0("0", dowlknum), 
                             TRUE ~ dowlknum)) %>% 
  local_to_nhdhr(from_colname = "lake_id", states = "mn") %>% 
  rename(site_id = nhdhr.id,
         total_zoop_samples = total_samples,
         min_zoop_year = min_year,
         max_zoop_year = max_year) 
  #this is removing a few problem lakes with site id/dow crosswalk
  # filter(!(site_id %in% c("106350457"))) %>% 
  # filter(dowlknum != "11041500") %>% 
  #selecting columns
  # select(site_id,
  #        dowlknum,
  #        total_zoop_samples,
  #        min_zoop_year,
  #        max_zoop_year)
#some level of difference between DOW and nhd here - Cass and Pike Bay get labeled in same nhd but different dows
#nhdhrs of 106350457, 120018379, 166868528 all have multiple "lake names" in a site id

# draw in more fish survey data?
cpe %>% 
  mutate(countycode = substring(lake_id, first = 1, last = 2)) %>% 
  group_by(lake_id, lake_name) %>% 
  summarise(maxyear = max(year)) %>%
  select(lake_id) %>% 
  pull() %>% 
  {dows <<- .}

surveys <- data.frame()

for (i in 1:length(dows)) {
  #i = 1
  surveys <- bind_rows(surveys,
            fishsurveydata(lakefinderdownload(dows[i])))
    
}

surveys %>% 
  filter(year(Date) > 2022) %>% 
  group_by(year(Date)) %>% 
  summarize(n_lakes = length(unique(LakeId)))

#wierd that 2023 surveys for ramsey co are not in lf yet:
surveys %>%
  mutate(countycode = substring(LakeId, first = 1, last = 2)) %>% 
  filter(countycode == "62") %>%
  filter(year(Date) > 2022) %>%
  group_by(year(Date)) %>%
  summarize(n_lakes = length(unique(LakeId)))


#make a 2023 surveys df
surveys %>% 
  filter(year(Date) > 2022) %>% 
  group_by(gear) %>% 
  count() %>% 
  print(n = 30)

surveys %>% 
  filter(year(Date) > 2022) %>% 
  group_by(LakeId,year(Date)) %>% 
  summarise_at("gear", toString) %>% 
  {surveys <<- .}

setDT(surveys)
setDT(cpe)
surveys[cpe, on = .(LakeId = lake_id), waterbody_name := lake_name ]

surveys %>% 
  rename(lake_id = LakeId,
         year = `year(Date)`) %>% 
  local_to_nhdhr(from_colname = "lake_id", states = "mn") %>% 
  rename(site_id = nhdhr.id) %>% 
  {surveys <<- .}

survey %>% 
  rename(gear = survey_components_proposed) %>% 
  mutate(year = 2024) %>% 
  {survey <<- .}

surveys <- bind_rows(survey, surveys)

rm(survey)

#this gives us 2023/2024 fish sampling. From here we will reshape to lakes as-rows format (fish year as a column), then add in the zoop years columns
setDT(surveys)
fish_surv <- surveys[ , .SD , .SDcols = c("waterbody_name","lake_id","site_id", "gear", "year", "survey_type") ]

fish_surv[is.na(gear) , gear := survey_type]
fish_surv[ , survey_type := NULL , ]
fish_surv[ , fish_surveyed := T , ]

#cast this wide (lakes as rows)
fish_surv <- dcast(fish_surv, waterbody_name + lake_id + site_id ~ year, value.var = c("fish_surveyed", "gear" ), fun.aggregate = toString)





#now use the ramsey data to make a zoops esque dataframe
# get a list of Ramsey County DOWs:
#white bear is 82016700, otter is 02000300, 

cpe %>% 
  mutate(countycode = substring(lake_id, first = 1, last = 2)) %>% 
  filter(countycode == "62") %>% 
  group_by(lake_id, lake_name) %>% 
  summarise(maxyear = max(year)) %>%
  select(lake_id) %>% 
  pull() %>% 
  c(.,"82016700", "02000300" )  %>%  
  {ramsey_dows <<- .}

# for reprex
# dput(ramsey_dows)
ramsey_dows <- c("62000100", "62000200", "62000500", "62000600", "62000700",
"62001002", "62001100", "62001300", "62001600", "62001800", "62002800",
"62003801", "62003802", "62003900", "62004600", "62004700", "62004800",
"62005400", "62005500", "62005600", "62005700", "62006100", "62006200",
"62006700", "62006900", "62007300", "62007500", "62007800", "62008000",
"62008200", "62008300", "62009500", "62017000", "62023100", "62027200",
"82016700", "02000300")


ramsey_zoops <- data.frame()

for (i in 1:length(ramsey_dows)) {
  #i = 1
  ramsey_zoops[i,1] = ramsey_dows[i]
  ramsey_zoops[i,2] = lakefinderdownload(ramsey_dows[i])$result$lakeName
    
}

colnames(ramsey_zoops) <- c("lake_id", "lake_name")

ramsey_zoops %>% 
  local_to_nhdhr(from_colname = "lake_id", states = "mn") %>% 
  {ramsey_zoops <<- .}
  
ramsey_zoops %>% 
  rename(site_id = nhdhr.id) %>% 
  {ramsey_zoops <<- .}

zoops %>% 
  filter(max_zoop_year > 2020) %>% 
  {zoops <<- .}
  
bind_rows(zoops, ramsey_zoops) %>% 
  {zoops <<- .}

rm(ramsey_zoops)

zoops %>% 
  mutate(zoop_sampled := T) %>% 
  {zoops <<- .}

setDT(zoops)

zoops[ , .N , lake_id][N>1]

lakes_data <- full_join(fish_surv, zoops)


lake_parameters <- full_join(secchi, temp, by = c("site_id")) 
lake_parameters <- full_join(lake_parameters, glm, by = c("site_id")) %>% 
  select(lake_name,
         site_id,
         centroid_lat,
         centroid_lon,
         everything())

lakes_data <- right_join(lake_parameters, lakes_data, by = c("site_id"))

rm(secchi, temp, glm, zoops, surveys, lake_parameters, fish_surv)


#mash in cpe
cpe %>% 
  group_by(lake_name, lake_id, species_1, sampling_method) %>% 
  summarize(
    n_obs = n(),
    n_years = length(unique(year(date))),
    mean_cpue = mean(cpue),
    median_cpue = median(cpue)
  ) %>% 
  setDT() %>% 
  {cpue_summary <<- .}

cpue_summary %>% 
  mutate(
    sampling_method = 
      case_when( sampling_method == "Standard 3/4-in mesh, double frame trap net sets" ~ "trap_net",
                 sampling_method == "Standard gill net sets" ~ "gill_net")
  ) %>% 
  {cpue_summary <<- .}

cpue_summary_wide <- dcast(cpue_summary, lake_name + lake_id ~ species_1 + sampling_method, value.var = c("mean_cpue"))

setDT(cpue_summary_wide)
setDT(lakes_data)

names(cpue_summary_wide)


lakes_data <- left_join(lakes_data, cpue_summary_wide)

lakes_data[is.na(waterbody_name), waterbody_name := lake_name.x ]
lakes_data[is.na(waterbody_name),  waterbody_name := lake_name.y ]

lakes_data[ , `:=` (lake_name.x = NULL, lake_name.y = NULL) , ]

names(lakes_data)

fwrite(lakes_data, file = "scripts&data/data/output/lake_chooser.csv" )




```


#cpe plots
```{r}
#looping through all
subset <- cpe %>% 
  filter(lake_id %in% survey$lake_id) %>% 
  #filter(lake_id %in% c("11020300", "48000200", "82016700")) %>% #for trial runs
  mutate(species_1 = case_when(species_1 == "largemouth_bass" ~ "largemouth",
                               TRUE ~ species_1),
         sampling_method = case_when(sampling_method == "Standard 3/4-in mesh, double frame trap net sets" ~ "Standard trap net sets",
                                     TRUE ~ sampling_method))

subset %>% 
  summarise(n_distinct(lake_id))
survey %>% 
  summarise(n_distinct(lake_id))
#missing 16 lakes from survey in cpe
#lakes that are missed 
missed_lakes <- survey %>% 
  filter(!(lake_id %in% subset$lake_id))
rm(missed_lakes)
#Owasso has the wrong dow in the survey object?
#one survey from the 2000s or older via lake finder in Bullhead, Bass, Net, Ten, Bower Trout, Silversack but not in cpe data
#no fish data via lake finder for Hen, Loon, Springer
#not standard gear in ram, daniels, duncan, Tioga, lac la croix
#Can't even find Carlson in lake finder 69074600


unique_lakes <- subset %>% select(lake_id, lake_name) %>% distinct()

# Loop through each unique lake and create a plot for each
for (i in 1:nrow(unique_lakes)) {
  lake_data <- subset %>% filter(lake_id == unique_lakes$lake_id[i])
  
  p <- lake_data %>% 
  group_by(lake_id, species_1, sampling_method) %>% 
  mutate(mins = min(cpue),
         maxs = max(cpue),
         ends = max(year(date)),
         quart1 = quantile(cpue, 0.25),
         quart2 = quantile(cpue, 0.75)) %>% 
  ungroup() %>% 
  ggplot() +
  geom_ribbon(aes(x = year(date), y = cpue, ymin = quart1, ymax = quart2), fill = 'grey90') +
  geom_line(aes(x = year(date), y = cpue, color = species_1), size = 0.7) +
  stat_smooth(aes(x = year(date), y = cpue), method = "lm", se = FALSE, lty = 2, lwd = 1, color = "black") +
  geom_point(data = . %>% filter(cpue == mins), aes(x = year(date), y = mins), color = "red", size = 4) +
  geom_point(data = . %>% filter(cpue == maxs), aes(x = year(date), y = maxs), color = "blue", size = 4) +
  geom_text(data = . %>% filter(cpue == mins), aes(x = year(date), y = mins, label = round(cpue, 2)), vjust = -1) +
  geom_text(data = . %>% filter(cpue == maxs), aes(x = year(date), y = maxs, label = round(cpue, 2)), vjust = 2.5) +
  ggtitle(paste(unique_lakes$lake_name[i], unique_lakes$lake_id[i])) +
  facet_grid(species_1 ~ sampling_method, scales = "free") +
  theme_tufte(base_size = 25, base_family = "Helvetica") +
  theme(axis.title = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks = element_blank(), 
        strip.text.y = element_text(size = 10), # Adjust text size for species_1
        legend.position = "none")
  
  # Display the plot
  print(p)
  
  # Save the plot to a file (optional)
  ggsave(filename = paste0(unique_lakes$lake_name[i], "_", unique_lakes$lake_id[i], ".png"), plot = p, width = 12, height = 8, bg = "white")
}

#intrested in pulling out a specific lake?
lake_data <- cpe %>% 
  filter(lake_id == "62005600")

lake_data %>% 
  group_by(lake_id, species_1, sampling_method) %>% 
  mutate(mins = min(cpue),
         maxs = max(cpue),
         ends = max(year(date)),
         quart1 = quantile(cpue, 0.25),
         quart2 = quantile(cpue, 0.75)) %>% 
  ungroup() %>% 
  ggplot() +
  geom_ribbon(aes(x = year(date), y = cpue, ymin = quart1, ymax = quart2), fill = 'grey90') +
  geom_line(aes(x = year(date), y = cpue, color = species_1), size = 0.7) +
  stat_smooth(aes(x = year(date), y = cpue), method = "lm", se = FALSE, lty = 2, lwd = 1, color = "black") +
  geom_point(data = . %>% filter(cpue == mins), aes(x = year(date), y = mins), color = "red", size = 4) +
  geom_point(data = . %>% filter(cpue == maxs), aes(x = year(date), y = maxs), color = "blue", size = 4) +
  geom_text(data = . %>% filter(cpue == mins), aes(x = year(date), y = mins, label = round(cpue, 2)), vjust = -1) +
  geom_text(data = . %>% filter(cpue == maxs), aes(x = year(date), y = maxs, label = round(cpue, 2)), vjust = 2.5) +
  ggtitle(paste(lake_data$lake_name, lake_data$lake_id)) +
  facet_grid(species_1 ~ sampling_method, scales = "free") +
  theme_tufte(base_size = 25, base_family = "Helvetica") +
  theme(axis.title = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks = element_blank(), 
        strip.text.y = element_text(size = 10), # Adjust text size for species_1
        legend.position = "none")
```

#lake parameter plots
```{r}
lake_parameters2024 <- survey %>% 
  left_join(lake_parameters, by = c("site_id"))

#talked about/ selected lakes
proposed.lakes <- data.frame(lake_id = c("11020300", #Leech
                                         "04003501", #Upper red
                                         "69037800", #Vermilion
                                         "34007900", #Green
                                         "18030800", #Pelican
                                         "11014700", #Winnibigoshish
                                         "16014300", #Devil Track
                                         "04003000", #Cass
                                         "39000200", #Lake of the Woods
                                         "48000200", # Mille Lacs
                                         "82016700", #White Bear
                                         "62000200", #Bald Eagle - no 2024 fish survey
                                         "25000100" #joining problem
                                         ))

lake_parameters2024 %>% 
  group_by(is.na(med_summer_secchi_meters),
           is.na(med_jul_temp),
           is.na(area)) %>% 
  count()
#looks like 284/329 lakes are good to go

lake_parameters2024 %>% 
  group_by(is.na(total_zoop_samples)) %>% 
  count()
#most lakes do not have zoops

problem_lakes <- lake_parameters2024 %>% 
  filter(is.na(med_summer_secchi_meters) |
           is.na(med_jul_temp) |
           is.na(area))
rm(problem_lakes)

#exploring missing secchi
miss_sec <- lake_parameters2024 %>% 
  filter(is.na(med_summer_secchi_meters) & !is.na(med_jul_temp) & !is.na(area)) %>% 
  select(lake_name, site_id, lake_id, parent_dow, basin_id)
rm(miss_sec)

#plot
lake_parameters2024 %>% 
  ggplot() +
  geom_point(aes(x = med_summer_secchi_meters, y = med_jul_temp, size = area)) +
  geom_point(data = lake_parameters2024 %>% filter(lake_id %in% proposed.lakes$lake_id),
               shape = 21, color = "black", fill = "yellow", alpha = 0.75, stroke = .5, aes(x = med_summer_secchi_meters, y = med_jul_temp, size = area,size = area)) +
  theme_base() +
  theme(legend.position = "none")

#interactive plot
p <- ggplot(lake_parameters2024, aes(x = med_summer_secchi_meters, y = med_jul_temp,
            alpha = .5,
                                     text = paste("Lake DOW:", lake_id, "<br>",
                                                  "Lake Name:", waterbody_name, "<br>",
                                                  "Secchi Depth (m):", med_summer_secchi_meters, "<br>",
                                                  "Size (km^2):", area, "<br>",
                                                  "July Temp (°C):", med_jul_temp, "<br>",
                                                  "# Zoop Samples:", total_zoop_samples, "<br>",
                                                  "Zoop Years:", min_zoop_year, "-", max_zoop_year))) +
  geom_point(shape = 21, color = "black", fill = "gray", alpha = 0.75, stroke = .5, aes(size = area)) +
  geom_point(data = lake_parameters2024 %>% filter(lake_id %in% proposed.lakes$lake_id),
               shape = 21, color = "black", fill = "yellow", alpha = 0.75, stroke = .5, aes(size = area)) +
  theme_base() +
  theme(legend.position = "none")
p_interactive <- ggplotly(p, tooltip = "text")
p_interactive
saveWidget(p_interactive, "Output/interactive_covary_lake_selection")

#looking at 2024 surveyed lakes compared to the rest
ggplot() +
  geom_point(data = lake_parameters %>%  filter(!is.na(lake_name)), aes(x = med_summer_secchi_meters, y = med_jul_temp, size = area)) +
  geom_point(data = lake_parameters2024, color = "red", aes(x = med_summer_secchi_meters, y = med_jul_temp, size = area,size = area)) +
  theme_base() +
  theme(legend.position = "none")
ggsave("Output/all_lakes_vs_2024survey.jpg")
```

#old code
```{r}
#lake parameters - joined from DOW, current code above uses DOW to get nhdhrid to join
secchi <- read_csv("Data/WQP_secchi_pull_20Mar2024.csv") %>% 
  select(MonitoringLocationIdentifier,
         ActivityStartDate,
         ResultMeasureValue,
         ResultMeasure.MeasureUnitCode) %>% 
  mutate(ResultMeasureValue = as.numeric(ResultMeasureValue)) %>% 
  filter(!is.na(ResultMeasureValue) & ResultMeasureValue >= 0) %>% 
  #Taking only MNPCA data and extracting DOW from monitoring location
  filter(str_detect(MonitoringLocationIdentifier, "^MNPCA-\\d{2}-\\d{4}-\\d{2}-\\d{3}$")) %>%
  mutate(DOW = str_replace_all(str_extract(MonitoringLocationIdentifier, "(?<=MNPCA-)\\d{2}-\\d{4}-\\d{2}"), "-", "")) %>% 
  #only keeping meter values
  filter(ResultMeasure.MeasureUnitCode == "m") %>% 
  rename(secchi_meters = ResultMeasureValue,
         date = ActivityStartDate) %>%
  mutate(year = year(date),
         month = month(date)) %>% 
  select(DOW,
         year,
         month, 
         secchi_meters) %>% 
  #creating values for this analysis 
  filter(year >= 2000 & month %in% c("6", "7", "8")) %>% 
  group_by(DOW) %>% 
  summarise(med_summer_secchi_meters = median(secchi_meters)) %>% 
  mutate(parent_dow = str_sub(DOW, 1,6),
         basin_id = str_sub(DOW, -2)) %>% 
  select(-DOW)
#I end up with median summer secchi (jun, jul, aug) values for years 2000 to present

glm <- read_csv("Data/glm_lake_metadata.csv") %>% 
  filter(state == "MN") %>% 
  select(site_id, lake_name, centroid_lon, centroid_lat, max_depth, area) %>% 
  mutate(site_id = str_remove(site_id, "^nhdhr_")) %>% 
  nhdhr_to_local(from_colname = "site_id", states = "mn") %>% 
  rename(DOW = local.id) %>% 
  group_by(site_id) %>% 
  slice_head(n =1) %>% 
  filter(!is.na(DOW)) %>% 
  mutate(parent_dow = str_sub(DOW, 1,6),
         basin_id = str_sub(DOW, -2)) %>% 
  select(-DOW)

temp <- read_feather("Data/lake_temperature_metrics_GLM_NLDAS.feather", col_select = NULL, as_data_frame = TRUE, mmap = TRUE) %>%
  select(site_id, year, mean_surf_jul) %>% 
  mutate(site_id = str_remove(site_id, "^nhdhr_")) %>% 
  nhdhr_to_local(from_colname = "site_id", states = "mn") %>% 
  rename(DOW = local.id)  %>%
  mutate(parent_dow = str_sub(DOW, 1,6),
         basin_id = str_sub(DOW, -2)) %>%
  #one to many join due to multiple basins in some lakes from an nhdhrid - taking only the first record of DOW for each NHD/year
  group_by(site_id, year) %>% 
  slice_head(n =1) %>% 
  filter(year >= 2000) %>% 
  group_by(site_id) %>% 
  summarise(med_jul_temp = median(mean_surf_jul)) %>% 
  filter(!is.na(DOW)) %>% 
  select(-DOW)
#I end up with a median jul surf temp for all years 2000-present for lakes - this is nhd level data so I just took first DOW
  
#sending IDs to heidi for zoops
survey_send <- survey %>% 
  rename(DOW_clean = lake_id,
         nhdhr_id = site_id) %>% 
  mutate(DOW_clean = paste0("mndow_", DOW_clean)) %>% 
  select(DOW,
         DOW_clean,
         parent_dow,
         basin_id,
         nhdhr_id,
         everything())
write_csv(survey_send, "pelo_2024_fish_surveyed_lakelist.csv")
```

